%-------------------------------------------------------------------------------
% This file contains the title, author and abstract.
% It also contains all relevant document numbers used for an ATLAS note.
%-------------------------------------------------------------------------------

% Title
\AtlasTitle{DiHiggs HH multilepton full Run2}

% Draft version:
% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
\AtlasVersion{0.1}

% Abstract - % directly after { is important for correct indentation
\AtlasAbstract{%
  This is a bare bones ATLAS document. Put the abstract for the document here.
}

% Author - this does not work with revtex (add it after \begin{document})
\author{The ATLAS Collaboration}

\AtlasAuthorContributor{Merve Nazlim Agaras}{d}{Int. note editor. Group framework developer and coordinator. Fit contact.}
\AtlasAuthorContributor{Xiaohu Sun}{a}{HH -> yy + 2L: MC signal, statistical analysis}
\AtlasAuthorContributor{Abdualazem Fadol}{b}{HH--> yy + 1/2L, HH -->2LSS, object/event selection, software framework}
\AtlasAuthorContributor{Yaquan Fang}{b}{Analysis contact. HH--> yy + 1/2L, HH -->2LSS, object/event selection, software framework}
\AtlasAuthorContributor{Kaili Zhang}{b}{Combination liason. HH--> yy + 1/2L, HH -->2LSS, object/event selection, software framework}
\AtlasAuthorContributor{Djamel Eddine Boumediene}{d}{QMisID DD estimates. Supervisor of Merve Nazlim Agaras.}
\AtlasAuthorContributor{Maosen Zhou}{b}{HH--> yy + 1/2L, HH -->2LSS, object/event selection, software framework}
\AtlasAuthorContributor{Weiming Yao}{c}{HH -> 1L + jets / 2had taus + jets: Tau selection and fakes}
\AtlasAuthorContributor{Rohin Narayan}{e}{HH -> 2L/3L: Fake leptons, kinematic discriminants, software framework} 
\AtlasAuthorContributor{Allison McCarn Deiana}{e}{HH -> 2L/3L: Fake leptons, kinematic discriminants, software framework}
\AtlasAuthorContributor{Xingguo Li}{f}{HH -> 2/3L + jets}
\AtlasAuthorContributor{Chihao Li}{g}{HH -> 4L + 2b: MC generation, object definition, event selection, combination}
\AtlasAuthorContributor{Yusheng Wu}{g}{HH -> 4L + 2b: MC generation, object definition, event selection, combination}
\AtlasAuthorContributor{Bartlomiej Zabinski}{h}{HH -> taus + X: Tau optimisation, machine learning, fit, framework}
\AtlasAuthorContributor{Anna Kaczmarska}{h}{HH -> taus + X: Tau optimisation, machine learning, fit, framework}
%\AtlasAuthorContributor{Ana Elena Dumitriu}{j, i}{Support in group framework 1.} Tiesheng Dai, Hang Qi, Bing Li, Bing Zhou
\AtlasAuthorContributor{Tiesheng Dai}{i}{HH -> 4L + 2b: MC signal, object definition, event selection, interpretation, combination}
\AtlasAuthorContributor{Hang Qi}{i}{HH -> 4L + 2b: MC signal, object definition, event selection, interpretation, combination}
\AtlasAuthorContributor{Bing Zhou}{i}{HH -> 4L + 2b: MC signal, object definition, event selection, interpretation, combination}
\AtlasAuthorContributor{Huirun Chen}{j}{HH->1L+3tau had: MC signal production, truth studies}
\AtlasAuthorContributor{Xiaozhong Huang}{j}{HH->1L+3tau had: MC signal production, truth studies}
\AtlasAuthorContributor{Bowen Zhang}{j}{HH->1L+3tau had: MC signal production, truth studies}
\AtlasAuthorContributor{Lei Zhang}{j}{HH->1L+3tau had: MC signal production, truth studies}
\AtlasAuthorContributor{Liang Li}{k}{HH -> 2/3L + jets}
\AtlasAuthorContributor{Jiannan Tang}{k}{HH -> 2/3L + jets}
\AtlasAuthorContributor{Lebohang Mokoena}{l}{X -> SH -> 2L + jets: MC signal, event selection, bkg estimation, statistical analysis}
\AtlasAuthorContributor{Bruce Mellado}{l}{X -> SH -> 2L + jets: MC signal, event selection, bkg estimation, statistical analysis}
\AtlasAuthorContributor{Lehumo Mashishi}{l}{X -> SH -> 2L + jets: MC signal, event selection, bkg estimation, statistical analysis}
\AtlasAuthorContributor{Jeremiah Kgomotso Monnakgotla}{l}{X -> SH -> 2L + jets: MC signal, event selection, bkg estimation, statistical analysis}
%\AtlasAuthorContributor{Dylan Kisliuk}{f}{Tau fake estimates.}
\AtlasAuthorContributor{Yesenia Hernandez}{l}{Analysis contact. X -> SH -> 2L + jets: MC signal, event selection, bkg estimation, statistical analysis}

\affil[a]{Manchester}
\affil[b]{Beijing IHEP	}
\affil[c]{Berkeley LBNL	}
\affil[d]{LPC Clermont-Ferrand}
\affil[e]{Dallas SMU}
\affil[f]{DESY}
\affil[g]{USTC}
\affil[h]{Krakow IFJ PAN}
\affil[i]{Michigan}
\affil[j]{Nanjing}
\affil[k]{Shanghai}
\affil[l]{Witwatersrand}






% Authors and list of contributors to the analysis
% \AtlasAuthorContributor also adds the name to the author list
% Include package latex/atlascontribute to use this
% Use authblk package if there are multiple authors, which is included by latex/atlascontribute
% \usepackage{authblk}
% Use the following 3 lines to have all institutes on one line
% \makeatletter
% \renewcommand\AB@affilsepx{, \protect\Affilfont}
% \makeatother
% \renewcommand\Authands{, } % avoid ``. and'' for last author
% \renewcommand\Affilfont{\itshape\small} % affiliation formatting
% \AtlasAuthorContributor{First AtlasAuthorContributor}{a}{Author's contribution.}
% \AtlasAuthorContributor{Second AtlasAuthorContributor}{b}{Author's contribution.}
% \AtlasAuthorContributor{Third AtlasAuthorContributor}{a}{Author's contribution.}
% \AtlasContributor{Fourth AtlasContributor}{Contribution to the analysis.}
% \author[a]{First Author}
% \author[a]{Second Author}
% \author[b]{Third Author}
% \affil[a]{One Institution}
% \affil[b]{Another Institution}


% If a special author list should be indicated via a link use the following code:
% Include the two lines below if you do not use atlasstyle:
% \usepackage[marginal,hang]{footmisc}
% \setlength{\footnotemargin}{0.5em}
% Use the following lines in all cases:
% \usepackage{authblk}
% \author{The ATLAS Collaboration%
% \thanks{The full author list can be found at:\newline
%   \url{https://atlas.web.cern.ch/Atlas/PUBNOTES/ATL-PHYS-PUB-2016-007/authorlist.pdf}}
% }

% ATLAS reference code, to help ATLAS members to locate the paper
\AtlasRefCode{ANA-HDBS-2019-04}

% ATLAS note number. Can be an COM, INT, PUB or CONF note
\AtlasNote{ANA-HDBS-2019-04-INT1}
